Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-03 tex/sections/intro.tex
Fix more readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities which could be used by an
adversary to catastrophically attack the consensus protocol. For example, a malware using a common zero-day
vulnerability might be able to infect a large portion of normal personal computers. This malware could be used by an
adversary to control the majority of participant computers in the consensus protocol and compromise the security of the
blockchain.

@@

To overcome these difficulties, Argennon uses a hybrid Proof of Stake consensus protocol. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the blockchain. Each
minted block is required to get approved by its corresponding validator assembly. Assemblies are very large sets of
validators including at least three percent of the total stake of the system. A block is approved if it gets
approval votes from at least \(2/3\) of the total stake of its validator assembly.

>>>>

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities which could be used by an
adversary to catastrophically attack the consensus protocol. For example, if a malware, probably using a common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participant computers in the consensus and compromise the security of the
blockchain.

@@

To overcome these difficulties, Argennon uses a hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected
by the Argennon users and is responsible for minting new blocks of the blockchain. Each
minted block is required to get approved by its corresponding validator assembly. Assemblies are very large sets of
validators including at least three percent of the total stake of the system. A block is approved if it gets
approval votes from at least \(2/3\) of the total stake of its validator assembly.
